%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.9]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{11pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage{multicol} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Junjun Yin - vita},
	pdfauthor={Junjun Yin},
	pdfproducer={}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

% DOCUMENT
\begin{document}
{\LARGE Junjun Yin, Ph.D}
\begin{center}
\line(1,0){450}
\end{center}
\section*{Contact Information}

\begin{multicols}{2}
 \begin{flushleft}
Room 813, Oswald Tower\\
The Pennsylvania State University\\
University Park, PA, 16802, United States
\end{flushleft}
\columnbreak
\begin{flushright}
Phone: +1 217-819-6366\\[.1cm]
Email: \href{mailto:a.jyin@psu.edu}{jyin@psu.edu}\\[.1cm]
\textsc{url}: \href{https://yinjunjun.github.io}{https://yinjunjun.github.io}
\end{flushright}
\end{multicols}


%%\hrule
\section*{Current Position}
\begin{multicols}{2}
 \begin{flushleft}
\emph{Assistant Research Professor}\\
Social Science Research Institute\\
The Pennsylvania State University\\
\end{flushleft}
\columnbreak
\begin{flushright}
\emph{ICDS Associate}\\
Institute for Computational and Data Sciences\\
\end{flushright}
\end{multicols}
%%\hrule

\section*{Previous Position}
\emph{Postdoctoral Research Fellow}\\
CyberGIS Center for Advanced Digital and Spatial Studies\\
Department of Geography and Geographic Information Science\\
National Center for Supercomputing Applications (NCSA)\\
University of Illinois at Urbana-Champaign, IL, USA
%%\hrule
\section*{Research Interests}
GIScience; Spatial Analysis and Modeling; Urban Informatics; Computational Geography;
Geo-Complexity and Human Mobility; (Geo)Visual-Analytics and Data Mining; 
GeoSpatial Big Data; GeoComputing; Spatial Interaction; High-performance (cyberGIS), Web and Mobile GIS

%\hrule
\section*{Education}
\noindent
\years{2009 - 2013}\textit{Ph.D} in Spatial Information Science, Dublin Institute of Technology, Ireland\\
Scince Fundation Ireland Scholarship\\
\textit{Advisors: Dr. James D. Carswell (Dublin Institute of Technology), Dr. Michela Bertolotto (University College Dublin)}\\
\years{2006 - 2009}\textit{MSc} in Geoinformatics, University of Gävle, Sweden\\
\textit{Advisor: Dr. Bin Jiang (University of Gävle)}\\
\years{2002 - 2006}\textit{BSc} in Electronics Engineering, University of Electronic Science and Technology of China

%%\hrule
\section*{Academic Experience}
\noindent
\years{2017-}Social Science Big Data Research Scientist, Pennsylvania State University, USA\\
\years{2016} Lecturer, Department of Geography and Geographic Information Science; University of Illinois at Urbana-Champaign, USA\\
\years{2014-2016} Postdoctoral Research Associate, CyberGIS Center for Advanced Digital and Spatial Studies; National Center for Supercomputing Applications; University of Illinois at Urbana-Champaign, USA\\
\years{2013-2014} Assistant Lecturer, Dublin Institute of Technology, Ireland\\
\years{2007-2008} Research Assistant, Hong Kong Polytechnic University, Hong Kong SAR, China

\section*{Research Grants and Projects}
\textbf{PI}. ``Identifying Discrimination During COVID-19 Pandemic on Twitter'',  ICDS (Institute for Computational and Data Sciences) COVID-19 explore grant, $\$$50,000. Project dates: 07/01/2020—06/30-2022\\
\textbf{Co-PI}. ``Are we more willing to speak up through mobile phones?  A comparison of desktop vs. mobile political sharing on Facebook''. SSRC (Social Science Research Council) grant, $\$$49,017. Project dates: 02/01/2020—01/31-2021\\
\textbf{Senior Personnel}. ``Pursuing Opportunities for Long-term Arctic Resilience for Infrastructure and Society''. NSF (National Science Foundation) NNA grant, $\$$3,000,000. Project dates: 01/01/2020—12/31-2022\\
\textbf{Co-PI}. ``RR: The Generalizability and Replicability of Twitter Data for Population Research''. NSF (National Science Foundation) SOC grant, $\$$500,000. Project dates: 07/15/2018—06/30-2021\\
\textbf{Co-PI}. ``Understanding National Park Visitors’ Spatial Behavior with Twitter Data''. Penn State Seed Grant (SSRI, ICS, and IST), $\$$20,000. Project dates: 03/01/2019—02/28-2021\\
\textbf{PI}. ``Data Science: Mining sequential mobility patterns from semantic Twitter user trajectories''. Microsoft Azure Data Science Research Award, $\$10,000$. Project dates: 05/01/2018—04/30/2019\\
\textbf{Co-PI}. ``An Innovative Approach to Tackle the Opioid Epidemic: Utilizing Twitter Data and Integrating Big Data Analytics and Spatial and Social Network Analyses'. Social Science Research Institute Level 2 Research Award, $\$$20,000. Project dates: 09/01/2018—08/30-2020\\
\textbf{Co-I}. ``Cognitive Changes Associated with Hormonal Treatment for Breast Cancer''. Health $\&$ Environment initiative seed grant award, $\$$49,972. Project dates: 07/01/2017—06/30-2019\\
\textbf{Co-PI}. ``The Generalizability and Replicability of Twitter Data for Population Research''. ICS seed grant award, $\$$35,000. Project dates: 07/01/2018—06/30-2019\\
\textbf{Co-PI}. ``Ecological Migration in a Large-Scale Quasi-Experiment Design in China: Implications of Climate Change, Landscape Structure, Ecosystem Services and Government Intervention''. IEEE seed grant award, $\$$25,000. Project dates: 04/15/2017—06/30-2018\\
\textbf{PI}. ``Mining Twitter User Demographics as a First-Step in Big Data for Population Research''. XSEDE (Extreme Science and Engineering Discovery Environment) Startup computational resource allocation award, 50,000 SUs $\&$ 40 TB storage (estimated $\$$2,794.78). Project dates: 03/27/2017—03/26-2019\\
\textbf{PI}. ``A cloud computing enabled GIS platform for the integration and synthesis of multi-layer geospatial data sources in urban studies: Understanding urban dynamics from geospatial Big Data''. Microsoft Azure Data Science Research Award, $\$20,000$. Project dates: 12/04/2016—12/03/2017\\
\textbf{SP/Research Scientist}. ``Activity space contexts and measuring environmental exposure in behavioral research''. R21 NCI grant (ASCMEE Study).

\section*{Publications}
%\subsection*{Work in progress}
%\years{2019}\textbf{Yin, J.} and Chi, G. (2017). A tale of three cities: A GIS-based data synthesis approach to integrating geographic context for understanding spatiotemporal activities in the urban environment. \textit{manuscript ready}
\subsection*{Submitted}
\years{2020} \textbf{Yin, J.}, Gao, Y.. Chi, G. and Van Hook, J., An Evaluation of Geo-located Twitter Data for Measuring Human Migration. (\textit{submitted to Annals of the Association of American Geographers})\\
\years{2020}Zheng, K., \textbf{Yin, J.}, Liu, M., Zhang, M. and Xie, M., A joint neural network model for geographical entity relation extraction from Chinese texts. (\textit{submitted to Knowledge and Information Systems})\\
\years{2020} \textbf{Yin, J.} and Chi, G., Understanding Spatiotemporal Urban Activity Patterns: A GIS-based Data Synthesis Approach. (\textit{In preparation})\\
\years{2020}Chi, G., \textbf{Yin, J.}, Van Hook, J., Plutzer, E. and Xu, H. The Mis-representativeness of Twitter Data. (\textit{In preparation})\\
\years{2020} \textbf{Yin, J.},  Brooks, M., Wang, D. and Chi, G., Characterizing Climate-Change Sentiment in Alaska with Twitter Data. (\textit{In preparation})\\
\subsection*{Peer Reviewed Journals}
\noindent
\years{2020}\textbf{Yin, J.} and  Chi, G., Characterizing People’s Daily Activity Patterns in the Urban Environment: A mobility network approach with geographic context-aware Twitter data. \textit{Annals of the Association of American Geographers}, (forthcoming)\\
\years{2020}Abdar, M., Basiri, M.E., \textbf{Yin, J.}, Asadi, S. and Chi, G., Energy Choices in Alaska: Mining People's Perception and Attitudes from Geotagged Tweets. \textit{Renewable $\&$ Sustainable Energy Reviews}, 124, p.109781\\
\years{2019}Pu, Y., Zhao, X., Chi, G., Zhao, S., Wang, J., Jin, Z. and \textbf{Yin, J.} (2019). Design and implementation of a parallel geographically weighted k-nearest neighbor classifier. \textit{Computers $\&$ Geosciences}, 127, pp. 111-122\\
\years{2018}Gao, Y., Wang, S. Padmanabhan, A., \textbf{Yin, J.} and Cao, G. (2018). Mapping Spatiotemporal Patterns of Events Using Social Media: A Case Study of Influenza Trends. \textit{International Journal of Geographical Information Science}, 32(3), pp. 425-449\\
\years{2017}\textbf{Yin, J.}, Soliman, A., Yin, D. and Wang, S. (2017). Delineate Urban Boundaries in Great Britain from the Network of Large Scale Twitter User Spatial Interactions. \textit{International Journal of Geographical Information Science}, 31(7), pp. 1293-1313\\
\years{2017}Soliman, A., Soltani, Q., \textbf{Yin, J.}, Padmanabhan, A., and Wang, S (2017). Social sensing of urban land use based on analysis of Twitter users' mobility patterns. \textit{PLoS ONE}, 12(7): e0181657. DOI:10.1371/journal.pone.0181657\\
\years{2017}Zheng, K., Kwan, M.P., Fang, L., \textbf{Yin, J.}, Gu, D. and Fu, Y. (2017). A Topology-concerned Spatial Vector Data Model for Column-oriented Databases. \textit{International Journal of Database Theory and Application}, 10(5), pp. 33-46\\
\years{2016}\textbf{Yin, J.}, Gao, Y., Du, Z. and Wang, S. (2016). Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach. \textit{ISPRS International Journal of Geo-Information}, 5(10):187.\\
\years{2016}Jiang, B., Ma, D., \textbf{Yin, J.} and Sandberg, M. (2016). Spatial Distribution of Tweet Numbers and Densities in Cities. \textit{Geographical Analysis}, 48(3), pp. 337-351\\
\years{2015}Jiang, B.,\textbf{Yin, J.} and Liu, Q. (2015). Zipf's Law for All the Natural Cities around the World. \textit{International Journal of Geographical Information Science, 29(3), pp. 498-522}\\
\years{2014}Jiang, B. and \textbf{Yin, J}. (2014). Ht-Index to Quantify the Fractal or Scaling Structure of Geographic Features. \textit{Annals of the Association of American Geographers}, 104(3), pp. 530–540\\
\years{2013}\textbf{Yin, J.} and Carswell, J.D. (2013). Spatial Search Techniques for Mobile 3D Queries in Sensor Web Environments. \textit{ISPRS International Journal of Geo-Information}, 2(1): pp.135-154\\
\years{2010}Carswell, J. D., \textbf{Yin, J.} and Gardiner, K. (2010). 3DQ: Threat Dome Visibility Querying on Mobile Devices \textit{GIM International}, 24(8)\\
\years{2010}Carswell, J.D., Gardiner, K. and \textbf{Yin, J.} (2010). Mobile Visibility Querying for LBS. \textit{Transactions in GIS}, 14(6): pp. 791-809, Wiley online library\\
\years{2009}Jiang, B., \textbf{Yin, J.} and Zhao, S. (2009). Characterizing the human mobility pattern in a large street network. \textit{Physical Review E}, 80(2), 021136\\
\years{2008}Jiang, B., Zhao, S. and \textbf{Yin, J.} (2008). Self-organized natural roads for predicting traffic flow: a sensitivity study. \textit{Journal of statistical mechanics: Theory and experiment}, P07008, IOP Publishing

\subsection*{Peer Reviewed Conferences and Lecture Notes}
\noindent
\years{2020}Liang, Y., \textbf{Yin, J.}, Pan, B., Chi, G., Andris, C., Miller, Z., Jorgenson, J. and Nickerson, N. (2020). Understanding Demographics and Experience of Tourists in Yellowstone National Park through Social Media. Travel and Tourism Research Association: Advancing Tourism Research Globally. 54 \\
\years{2019}\textbf{Yin, J.}, and Chi, G. (2019). Understanding Spatiotemporal Urban Activity Patterns with Geo-located Twitter data: A GIS-based Synthesis Approach. \textit{66th Annual North American Meetings of the Regional Science Association International (NARSC)}, November 13-16, 2019, Pittsburg, Pennsylvania\\
\years{2019}\textbf{Yin, J.}, and Chi, G. (2019). An Evaluation of Geo-located Twitter Data as Indicators for Human Migration. \textit{IUSSP Research Workshop on Digital Demography in the Era of Big Data}, June 6-7, 2019, Seville, Spain\\
\years{2019}Chi, G., \textbf{Yin, J.}, Van Hook, J., Plutzer, E. and Heng, X. (2019). The Generalizability of Twitter Data for Population Research. \textit{Population Association of America (PAA) Annual Meeting}, April 22-25, Washington, DC, USA\\
\years{2018}\textbf{Yin, J.}, Chi, G. and Van Hook, J. (2018). Evaluating the Representativeness in the Geographic Distribution of Twitter User Population. \textit{The 12th Workshop on Geographic Information Retrieval in ACM SIGSPATIAL 2018}, November 6-9, 2018, Seattle, Washington, USA\\
\years{2018}Jeong, M., \textbf{Yin, J.}, and Wang, S. (2018). Outliers Detection and Comparison of Origin-Destination Flows with Data Depth. \textit{The 10th International Conference on Geographic Information Science (GIScience 2018)}, August 28-31, 2018, Melbourne, Australia\\
\years{2017}\textbf{Yin, J.} (2017). Mining sequential mobility pattern from semantics enriched Twitter user trajectories. \textit{NSF Mobility Workshop on Analyzing Movement and Mobility within Geographic Context}, May 11-12, 2017, The Ohio State University, Columbus, Ohio\\
\years{2017}Chi, G., \textbf{Yin, J.} and Hook, J.V. (2017). Predicting Twitter User Demographics as a First Step in Big Data for Population Research. \textit{The 28th International Population Conference of the International Union for the Scientific Study of Population}, October 29-November 4, 2017, Cape Town, South Africa\\
\years{2016}\textbf{Yin, J.}, Lu, B., Yin, D. and Wang, S. (2016). A scalable visual-analytics approach for studying mobility networks: Revealing hierarchical structures in taxi mobility flows of New York, \textit{The Third International Conference on CyberGIS and Geospatial Data Science}, July 26-28, 2016, Urbana, Illinois\\
\years{2016}\textbf{Yin, J.}, Gao, Y. and Wang, S. (2016). Urban Sensing from Volunteered Citizen Participation using Mobile Devices. In \emph{Seeing Cities through Big Data: Research, Methods and Applications in Urban Informatics}, Springer\\
\years{2015}Soliman, A., \textbf{Yin, J}, Soltani, K., Padmanabhan, A., and Wang, S. (2015). Where Chicagoans tweet the most: Semantic analysis of preferential return locations of Twitter users, \textit{1st International Workshop on Smart Cities and Urban Analytics 2015, 23rd ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems}\\ 
\years{2014}\textbf{Yin, J.} and Wang, S. (2014). Understanding the Evolvements of Natural Cities from Nighttime Light Images: A CyberGIS-Enhanced Approach to Large Scale Geospatial Data Analysis, \textit{The Second International Conference on CyberGIS and Geodesign}, August 19-21, 2014, Redlands, California\\
\years{2014}\textbf{Yin, J.}, Gao, Y. and Wang, S. (2014). CyberGIS Enabled Urban Sensing from Volunteered Citizen Participation using Mobile Devices. \textit{NSF Workshop on Big Data and Urban Informatics 2014}\\
\years{2013}Truong-Hong, L., Thi, T.T.P, \textbf{Yin, J.} and Carswell, J.D. (2013). Detailed 3D building models for Google Earth integration. In \textit{Proceedings of the 13th International Conference on Computational Science and Its Applications (ICCSA 2013)}, Ho Chi Minh City, Vietnam: Springer (\textbf{\emph{$*$Best paper award}})\\
\years{2013}Thi, T.T.P, Truong-Hong, L., \textbf{Yin, J.} and Carswell, J.D. (2013). Exploring Spatial Business Data: A ROA based eCampus application. In \textit{Proceedings of the 11th International conference on Web and Wireless Geographical Information Systems}, Banff, AB: Springer Berlin Heidelberg, pp. 164-179\\
\years{2012}\textbf{Yin, J.} and Carswell, J.D. (2012). Effects of Variations in 3D Spatial Search Techniques on Mobile Query Speed vs Accuracy. \textit{Web and Wireless Geographical Information Systems}, Naples, Italy. (\textbf{\emph{$*$Best paper award}})\\
\years{2012}Carswell, J.D. and \textbf{Yin, J.} (2012). Mobile Spatial Interaction in the Future Internet of Things. In \textit{Proceedings of the 20th International Conference on Geoinformatics (GEOINFORMATICS)}, 2012, pp. 1-6\\
\years{2012}\textbf{Yin, J.} and Carswell, J.D. (2012). MobiSpatial: Open-source for Mobile Spatial Interaction. \textit{Proceedings of the 27th Annual ACM Symposium on Applied Computing}, pp. 572-573\\
\years{2012}\textbf{Yin, J.} and Carswell, J.D. (2011). Touch2Query enabled mobile devices: A case study using OpenStreetMap and iPhone. \textit{Web and Wireless Geographical Information Systems}, pp. 203-218, Springer\\
\years{2009} Gardiner, K., \textbf{Yin, J.} and Carswell, J.D. (2009). EgoViz: A mobile based spatial interaction system. \textit{Web and Wireless Geographical Information Systems}, pp. 135-152, Springer
\subsection*{Books}
\years{2009} \textbf{Yin, J.} (2009), \emph{The Topological Patterns of Urban Street Networks: Exploring the topological patterns of urban street networks from analytical and visual perspectives}, VDM: Germany, ISBN: 3639161734

\subsection*{Invited talks}
\years{2020}Yin, J. (2020). Uncovering universal human activity patterns with geospatial big data: complexity,unity, and regularity. Mar, 2020, Auburn University, Auburn, AL, USA\\
\years{2020}Yin, J. (2020). Computational Social Sciences: spatial interactions and geo-complexity. Feb, 2020, University of Arkansas, Fayetteville, AR , USA\\
\years{2019}Yin, J. (2019). Spatial Networks: A computational geography approach to new insights into spatial interactions and geo-complexity. Jan, 2019, University of Florida, Gainesville, FL , USA\\
\years{2018}Yin, J. (2018). Computational Geography for Capturing Geo-Complexity in Urban Studies. June, 2018, Newcastle University, Newcastle upon Tyne, UK\\
\years{2018}Yin, J. (2018). Advanced Methods and Techniques for Big GeoData. June, 2018, ITC, University of Twente, Enschede, the Netherlands\\
\years{2018}Yin, J. (2018). Geo-Complexity and Human mobility: Through the lens of spatial Big Data to understand urban dynamics. February, 2018, University of Denver, Denver, USA\\
\years{2018}Yin, J. (2018). High-performance Computing with Hadoop. Software in the Humanities and Social Sciences Workshop. February, 2018, Penn State, University Park, USA
\subsection*{Presentations}
\years{2018}Yin, J. (2018). Spatial Interaction Patterns of Preferential Return Behaviors in People’s Daily Life. The Association of American Geographers Annual Meeting, April 10-14, 2018, New Orleans, Louisiana, USA\\
\years{2017}Yin, J. (2017). A mobility network approach to modeling urban spatial interactions: Insights from the movement Big Data in New York City. The Association of American Geographers Annual Meeting, April 5-9, 2016, Boston, Massachusetts, USA\\
\years{2016}Yin, J. and Wang, S. (2016). Mining Mobility Patterns From Semantic Twitter User Trajectories. The Association of American Geographers Annual Meeting, March 29-April 2, 2016, San Francisco, California, USA\\
\years{2015}Yin, J. and Wang, S. (2015). Finding community structures of UK cities based on large-scale Twitter user mobility patterns, \textit{Association of American Geographers Annual Meeting, Chicago, 2015}, April 21-25, 2015, Chicago, Illinois, USA\\
\years{2011}Yin, J. (2011). Web-service based Mobile Geospatial Application Development using Python, \textit{PyCon 2011}, Dublin, Oct 8-9

\section*{Teaching Experience as Instructor}
\years{2016 - } GEOG 479: Advanced Topics in GIS -- CyberGIS, Spring, 2016, \textit{Lecturer}, Department of Geography and Geographic Information Science, UIUC\\
\years{2015 - } Parallel Databases, \textit{workshop/short course series}, CyberGIS Center, UIUC\\
\years{2015 - } Interactive Visualization of Large-scale Movement Data using Apache Spark, \textit{Summer school series}, CyberGIS Center, UIUC\\
\years{2015 - } Introducing the CyberGIS Toolkit in high performance computing environment, \textit{workshop/short course series}, CyberGIS Center, UIUC\\
\years{2015 - } Taming with geospatial Big Data with Hadoop, \textit{workshop/short course series}, CyberGIS Center, UIUC\\
\years{2014 - } Getting to know CyberGIS, \textit{workshop/short course series}, CyberGIS Center, UIUC\\
\years{2014 - 2016} Education and outreach at the CyberGIS Commons, \textit{Lead}, University of Illinois at Urbana-Champaign, 2014 - 2016\\
\years{2013} Programming in C, \textit{assistant lecturer}, Dublin Institute of Technology, 2013 - 2014\\
\years{2013} Object oriented programing for game development, \textit{senior demonstrator/assistant lecturer}, Dublin Institute of Technology, 2013 - 2014\\
\years{2013} User interface design and GUI programing with Java, \textit{senior demonstrator/assistant lecturer}, Dublin Institute of Technology, 2013 - 2014

%\hrule
\section*{Skills}
Programing languages:Java, Python, Objective-C, Matlab, R, JavaScript, NoSQL\\
High performance computing: Apache Hadoop, Apache Spark, MongoDB\\
Mobile and Web development: iOS and Android, Cesium 3D Globe, D3.js\\
Spatial databases: PostGIS, Oracle Spatial, SpatiaLite, ArcGIS

%\hrule
\section*{Honors and Awards}
\noindent
\years{2013}\emph{Fiosraigh Head of School Research Award}: for excellence in research, Dublin Institute of Technology\\
\years{2013}\emph{EU Future Internet Award}: for excellence in Future Internet research\\
\years{2009}\emph{PhD scholarship from Science Foundation Ireland (SFI)}: StratAG PhD scholarship\\
\years{2006}\emph{Outstanding Graduate Student Award}: University of Electronic Science and Technology of China\\
\years{2006}\emph{Best Undergraduate Dissertation Award}: Department of Electronic Engineering, University of Electronic Science and Technology of China\\
\years{2005}\emph{National Undergraduate Electronic Design Contest: Second prize}:Embedded system for Multi-channel and frequency wave generating, (Team: Junjun Yin, Yu Chen, and Xia Yu)

%\hrule
\section*{Service to the Profession}
\subsection*{Guest editors}
Guest editor for Special Issue of ``Chinese Sociological Dialogue``: Spatiotemporal Big Data and Sustainable Social Development (2017)
\subsection*{Program Committees and Organizers}
\begin{itemize}
\item{\textbf{PC} member for W2GIS 2020: 18th International Symposium on Web and Wireless Geographical Information Systems, Wuhan, China, May 14-15, 2020}
\item{\textbf{Chair} for Innovations in Spatial Data Analysis and Modeling, 66th Annual North American Meetings of the Regional Science Association International (NARSC), Pittsburg, Pennsylvania, November 13-16, 2019}
\item{\textbf{PC} member for W2GIS 2019: 17th International Symposium on Web and Wireless Geographical Information Systems, Kyoto, Japan, May 16-17, 2019}
\item{\textbf{PC} member for International Conference on Location-based Social Media Data, March 5-7, 2015, Athens, Georgia, USA}
\item{\textbf{Co-chair} for Advances in Spatial Interaction Models and Methods in the Big Data Era I, Spatiotemporal Symposium, 2018 AAG Annual Meeting, New Orleans, April 10 – April 14, 2018}
\item{\textbf{Chair} for Big Movement Data for Geospatial Analytics on Urban Interactions, Symposium on Human Dynamics in Smart and Connected Communities, 2017 AAG Annual Meeting, Boston, Massachusetts, April 5 - April 9, 2017}
\item{\textbf{Chair} for Understanding Urban Dynamics Based on Movement Big Data, 2016 AAG Annual Meeting, San Francisco, California, March 29 - April 2, 2016}
\end{itemize}
\subsection*{Reviewer for Proposals}
\begin{itemize}
  \setlength\itemsep{0em}
  \item \emph{Methodology, Measurement, and Statistics Program, \textbf{National Science Foundation}} (2019)  
\end{itemize} 


\subsection*{Reviewer for Journals}
Has reviewed for \textbf{28} journals
\begin{itemize}
  \setlength\itemsep{0em}
  \item \emph{Annals of the American Association of Geographers} (2018-2019)  
  \item \emph{International Journal of Geographical Information Science (IJGIS)} (2010, 2014-2018)
  \item \emph{Applied Geography} (2020)  
  \item \emph{Journal of Geovisualization and Spatial Analysis} (2018)
  \item \emph{Cartography and Geographic Information Science} (2018)
  \item \emph{Computers, Environment and Urban Systems (CEUS)} (2009-2010, 2013-2019)
  \item \emph{Journal of Urban Technology} (2019-2020)
  \item \emph{Transactions on Intelligent Transportation Systems} (2019-2020)
  \item \emph{EPJ Data Science} (2017)
  \item \emph{Geomatica} (2018)
  \item \emph{GeoJournal} (2018)
  \item \emph{Chinese Sociological Dialogue} (2018)
  \item \emph{Spatial Information Research} (2018)
  \item \emph{Sensors} (2018)
  \item \emph{Geographical Analysis} (2016-2018)
  \item \emph{Cluster Computing} (2017-2020)
  \item \emph{Journal of Geographical Systems} (2016-2017)
  \item \emph{Demography} (2016-2019)
  \item \emph{Environment and Planning B: Planning and Design} (2016-2017)
  \item \emph{Science China Information Science} (2015)
  \item \emph{PLOS One} (2013-2020)
  \item \emph{Cities} (2014)
  \item \emph{ISPRS International Journal of Geo-Information} (2013-2020)
  \item \emph{Electronics} (2020)
  \item \emph{Journal of Location Based Services} (2013)
\end{itemize} 

\subsection*{Reviewer for Conferences}
\begin{itemize}
  \setlength\itemsep{0em}
  \item \emph{GIScience} (2014, 2016)
  \item \emph {UbiComp} (2016)
  \item \emph {W2GIS} (2019)
\end{itemize}
\vfill{}

\begin{center}
{\scriptsize  Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
%Available from \href{http://sites.google.com/site/yinjunjun/}{
%\fontspec{Times New Roman}
%\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
\href{https://yinjunjun.github.io}{Junjun Yin}}
\end{center}

\end{document}